SOL Filamentary transport: update from joint AUG-TCV MST1 experiment

### 2018-01-23 Meetings/25ITPADivSOL/vianello_25itpadivsol.tex
Still improving the tex file for ITPA

\begin{frame}{Motivation and deliverables}
  \Fontvi
  \vspace{-1cm}
  \begin{itemize}
    \item \alert{Relation between downstream divertor conditions and
        up-stream SOL profiles is not well understood. Influence of
        SOL blob structures on shoulder formation and divertor
        conditions is key element towards predictive
        capabilities. Joint effort within the EUROfusion framework to
        address this issue on all the MST1 devices (AUG, TCV and MAST-U)}
  \end{itemize}
  \onslide<2->{A series of deliverables are foreseen for 2017-2018 program
\begin{enumerate}
\item \only<3>{\color{ta3chameleon}} Cross-machine L-Mode
  shoulder dependence on current both at constant B$_t$ and at
  constant $q_{95}$. Rationale: disentangle the effect of current and
  parallel connection length
\item \only<3>{\color{taorange}}Establish robust scenario for density
  shoulder profile in H-Mode and establish dependence on
  fuelling/neutral profiles/divertor condition
\item \only<3>{\color{ta3chameleon}}Fluctuations mesurement on AUG to study
  filamentary transport under high-power H-Mode conditions \only<3>{\color{consorziored}}and under
  different plasma configurations (SN, DN)
\item \only<3>{\color{taorange}}Study the role of ELM regimes,  neutral
  compression and particle density in filamentary transport and
  related shoulder formation
\item \only<3>{\color{taorange}} Identify the contribution of
  collisionality and seeding on filamentary transport and related
  shoulder formation
\item \only<3>{\color{consorziored}}Determine the effect of filaments and
  shoulder formation on target heat loads in different H-mode plasmas
\end{enumerate}}
\onslide<3>{
I will report only on few of the deliverables since part of them will
be studied in forthcoming campaigns
}
\end{frame}

\begin{frame}{Current scan at constant B$_t$}
  \begin{columns}
    \begin{column}{0.6\textwidth}
      \includegraphics<1>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantBt}
      \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantBt}
      \includegraphics<3>[width=.9\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantBt}
      \includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NeutralsVsNe5IpConstantBt}
      \includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NeutralsVsGreenwaldConstantBt}
      \includegraphics<6>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/UpstreamTargetProfilesConstantBt}
      \includegraphics<7>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/ExampleShoulderAmplitude}
      \includegraphics<8>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsNe5IpConstantBt}
      \includegraphics<9>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsGreenwaldIpConstantBt}      
    \end{column}
    \begin{column}{0.4\textwidth}
      \begin{itemize}
        \item<1|only@1> Shape matched in within the single scan done for each of
          the machine
        \item<1|only@1> The scan implies a modification of the
          L$_{\parallel}$. AUG exhibit a parallel connection length
          which is 5 times smaller then TCV
        \item<2|only@2> AUG: Fueling reduced only at smaller current to
          avoid earlier disruption. Similar neutral pressure in the
          subdivertor region reached. NBI additional power added to
          keep power in the SOL approximately constant
        \item<3|only@3> TCV: Ohmic heating only. Similar neutral compression reached and
          D$_{\alpha}$ radiation from the floor. 
        \item<4|only@4> Divertor neutral density estimated starting
          from D$_{\alpha}$ calibrated camera and using electron
          density and temperature from LP data. Neutral density
          increases earlier in edge density at lower current
        \item<5|only@5> Neutrals behavior reconciled whenever
          comparison considered as a function of Greenwald fraction  
        \item<6|only@6> For both AUG and TCV flattening of normalized
          upstream profile reached \alert{earlier in density at lower
            current.} For both the machine the increase of $\lambda_n$
          reached for larger values of $\Lambda_{div}$
        \item<7|only@7> Quantifying profile evolution using the
          \alert{shoulder amplitude metric} introduce by Wynn and
          Lipschultz for JET. \alert{Amplitude is the difference
            between normalized upstream density profiles}
        \item<8-9> Amplitude evolve faster in density at lower
          current \onslide<9>{\alert{but once evolution \textit{vs} greenwald
            fraction is considered the evolution is equivalent between
          different current}}  
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}  
\end{document}

>>>>

\begin{frame}{Motivation and deliverables}
  \Fontvi
  \vspace{-1cm}
  \begin{itemize}
    \item \alert{Relation between downstream divertor conditions and
        up-stream SOL profiles is not well understood. Influence of
        SOL blob structures on shoulder formation and divertor
        conditions is key element towards predictive
        capabilities. Joint effort within the EUROfusion framework to
        address this issue on all the MST1 devices (AUG, TCV and MAST-U)}
  \end{itemize}
  \onslide<2->{A series of deliverables are foreseen for 2017-2018 program
\begin{enumerate}
\item \only<3>{\color{ta3chameleon}} Cross-machine L-Mode
  shoulder dependence on current both at constant B$_t$ and at
  constant $q_{95}$. Rationale: disentangle the effect of current and
  parallel connection length
\item \only<3>{\color{taorange}}Establish robust scenario for density
  shoulder profile in H-Mode and establish dependence on
  fuelling/neutral profiles/divertor condition
\item \only<3>{\color{ta3chameleon}}Fluctuations mesurement on AUG to study
  filamentary transport under high-power H-Mode conditions \only<3>{\color{consorziored}}and under
  different plasma configurations (SN, DN)
\item \only<3>{\color{taorange}}Study the role of ELM regimes,  neutral
  compression and particle density in filamentary transport and
  related shoulder formation
\item \only<3>{\color{taorange}} Identify the contribution of
  collisionality and seeding on filamentary transport and related
  shoulder formation
\item \only<3>{\color{consorziored}}Determine the effect of filaments and
  shoulder formation on target heat loads in different H-mode plasmas
\end{enumerate}}
\onslide<3>{
I will report only on few of the deliverables since part of them will
be studied in forthcoming campaigns. \textcolor{red}{Remember this is
  still a work in progress}
}
\end{frame}

\begin{frame}{Current scan at constant B$_t$}
  \begin{columns}
    \begin{column}{0.6\textwidth}
      \includegraphics<1>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantBt}
      \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantBt}
      \includegraphics<3>[width=.9\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantBt}
      \includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NeutralsVsNe5IpConstantBt}
      \includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NeutralsVsGreenwaldConstantBt}
      \includegraphics<6>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/UpstreamTargetProfilesConstantBt}
      \includegraphics<7>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/ExampleShoulderAmplitude}
      \includegraphics<8>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsNe5IpConstantBt}
      \includegraphics<9>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsGreenwaldIpConstantBt}      
      \includegraphics<10>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsLambdaIpConstantBt}
      \includegraphics<11>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldBlobAllColor}         
    \end{column}
    \begin{column}{0.4\textwidth}
      \begin{itemize}
        \item<1|only@1> Shape matched in within the single scan done for each of
          the machine
        \item<1|only@1> The scan implies a modification of the
          L$_{\parallel}$. AUG exhibit a parallel connection length
          which is 5 times smaller then TCV
        \item<2|only@2> AUG: Fueling reduced only at smaller current to
          avoid earlier disruption. Similar neutral pressure in the
          subdivertor region reached. NBI additional power added to
          keep power in the SOL approximately constant
        \item<3|only@3> TCV: Ohmic heating only. Similar neutral compression reached and
          D$_{\alpha}$ radiation from the floor. 
        \item<4|only@4> Divertor neutral density estimated starting
          from D$_{\alpha}$ calibrated camera and using electron
          density and temperature from LP data. Neutral density
          increases earlier in edge density at lower current
        \item<5|only@5> Neutrals behavior reconciled whenever
          comparison considered as a function of Greenwald fraction  
        \item<6|only@6> For both AUG and TCV flattening of normalized
          upstream profile reached \alert{earlier in density at lower
            current.} For both the machine the increase of $\lambda_n$
          reached for larger values of $\Lambda_{div}$
        \item<7|only@7> Quantifying profile evolution using the
          \alert{shoulder amplitude metric} introduce by Wynn and
          Lipschultz for JET. \alert{Amplitude is the difference
            between normalized upstream density profiles}
        \only<8-9>{\item Amplitude evolve faster in density at lower
          current in the far SOL \onslide<9>{\alert{but once evolution \textit{vs} greenwald
            fraction is considered the evolution is equivalent between
            different current}}}
        \item<10|only@10> Amplitude evolution still reconciled in AUG if
          considered as a function of local evolution of $\Lambda_{div}$
        \item<11|only@11> For both AUG and TCV $\lambda_n$ increases
          with blob size without significant difference within the
          current explored
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}{Current scan at constant q$_{95}$}
  \begin{columns}
    \begin{column}{0.6\textwidth}
      \includegraphics<1>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantQ95}
      \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}
      \includegraphics<3>[width=.9\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}
      \includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NeutralsVsGreenwaldConstantQ95}
      \includegraphics<5>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/UpstreamTargetProfilesConstantQ95}
      \includegraphics<6>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantQ95}
      \includegraphics<7>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsLambdaIpConstantQ95}
      \includegraphics<11>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldBlobAllColor}         
    \end{column}
    \begin{column}{0.4\textwidth}
      \begin{itemize}
        \item<1|only@1> Shape matched in within the single scan even
          though this required for TCV operation with very low
          toroidal field (0.8T)
        \item<1|only@1> The parallel connection length remains almost unchanged
        \item<2|only@2> AUG: As for the case of constant B$_t$ we have
          pretty reproducible behavior matching basically the plasma
          condition in within the current scan
        \item<3|only@3> TCV: Even at such an high density at lower
          current (and lower B$_t$) no sign of target ion flux
          rollover/detachment
        \item<4|only@4> AUG: Divertor neutral density exhibits still
          the same behavior is considered as a function of greenwald fraction
        \item<5|only@5> For AUG upstream and target profiles exhibit
          the same behavior with flattening observed at large values
          of $\Lambda_{div}$. TCV actually even at high value of
          density no sign of upstream profile flattening \alert{even
            at very large values of $\Lambda_{div}$}
        \item<6|only@6> This is due to the fact we did not reach
          divertor detachment which \alert{seems necessary for
            upstream profile modification}  
        \item<7|only@7> AUG: Amplitude evolution as a function of $\Lambda_{div}$ 
          still reconcile the explored current scan

      \end{itemize}
    \end{column}
  \end{columns}

\end{frame}

\end{document}
